Simultaneous Elicitation of Scoring Rule and Agents Preferences for Robust Winner Determination

### 2020-06-03 draft.tex
corrected table 3
Some comments

The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
This strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or a question about a preference ordering (unless the profile is already known entirely). If it opted for a question about weights, it draws one rank in $2 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$. The intervals are initialized to $[1, n]$. If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; picks an alternative $a$ randomly with equal probability among those involved in some incomparabilities in $\ppref_j$; and picks an alternative $b$ with equal probability among those incomparable with $a$ in $\ppref_j$.

@@

The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it to a small set of $n+1$ candidate questions: one per agent, and one to the chair. It uses the heuristic proposed by \citet{Lu2011} to define the candidate questions to the agents. Considering agent $j$, either $x^{*} \ppref_j \bar{y}$, or $\bar{y} \ppref_j x^{*}$, or $x^{*}$ and $\bar{y}$ are incomparable in $\ppref_j$. As shown in the proof of Claim \ref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as he can above $x^{*}$ in the first case, and between $\bar{y}$ and $x^{*}$ in the second. An intuitive way to reduce the pairwise max regret is, therefore, to directly ask questions involving such alternatives, hoping for an answer that would prevent the adversary to play his best game. If $x^{*}$ and $\bar{y}$ are incomparable, then we just ask the agent $j$ to compare them.
To define the candidate question to the chair, consider
%\begin{align}
$\w^\tau = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$,
%\end{align}
the weight vector that minimize the $\PMR$ in the worst case.
We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
We then evaluate, for each candidate question, the minimax regret for the two possible answers; finally we choose the best according to $\leximax$.

@@

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]r}
			\toprule
			{p} & {Two ph.} \\
			\midrule
			0 & 20.00 \\
			25 & 18.85 \\
			50 & 17.29 \\
			75 & 15.77 \\
			100 & 14.70 \\
			125 & 12.99 \\
			150 & 11.97 \\
			175 & 9.99 \\
			200 & 11.49 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Regret in problems of size $(10, 20)$ after $200$ questions (one repetition only).}
	\label{fig:p}
\end{table}

>>>>

The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
This strategy first decides with a probability of $1/2$ each whether it will ask a question about weights or a question about a preference ordering (unless the profile is already known entirely). If it opted for a question about weights, it draws one rank in $2 ≤ r ≤ m-2$ equiprobably \commentOC{Isn’t this $1 ≤ r$?}, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$. The intervals are initialized to $[1, n]$. If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.

@@

The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it to a small set of $n+1$ candidate questions: one per agent, and one to the chair. It uses the heuristic proposed by \citet{Lu2011} to define the candidate questions to the agents. Considering agent $j$, either $x^{*} \ppref_j \bar{y}$, or $\bar{y} \ppref_j x^{*}$, or $x^{*}$ and $\bar{y}$ are incomparable in $\ppref_j$. \commentOC{I think $\bar{y}$ is not defined.} As shown in the proof of Claim \ref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as he can above $x^{*}$ in the first case, and between $\bar{y}$ and $x^{*}$ in the second. An intuitive way to reduce the pairwise max regret is, therefore, to directly ask questions involving such alternatives \commentOC{(with equal likelyhood?)}, hoping for an answer that would prevent the adversary to play his best game. If $x^{*}$ and $\bar{y}$ are incomparable, then we just ask the agent $j$ to compare them.
To define the candidate question to the chair, consider
%\begin{align}
$\w^\tau = \argmin_{\w \in W} s(\bar{y}; \bar{\profile}, \w) - s(x^{*}; \bar{\profile}, \w)$,
%\end{align}
the weight vector that minimize the $\PMR$ in the worst case.
We compare $\bar{\w}$ and $\w^{\tau}$ component-wise to find the position $r$ that is most valuable to ask about (the one that maximizes $\abs{\bar{\w}_r - \w^{\tau}_r}$), and choose $\lambda$ as the middle of the interval of possible values for that rank.
We then evaluate, for each candidate question, the minimax regret for the two possible answers; finally we choose the best according to $\leximax$.

@@

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]r}
			\toprule
			{p} & {Two ph.} \\
			\midrule
			0 & 11.49 \\
			25 & 9.99 \\
			50 & 11.97 \\
			75 & 12.99 \\
			100 & 14.70 \\
			125 & 15.77 \\
			150 & 17.29 \\
			175 & 18.85 \\
			200 & 20.00 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Regret in problems of size $(10, 20)$ after $200$ questions (one repetition only).}
	\label{fig:p}
\end{table}
